Making Sequential Programs Deterministic

### 2019-03-31 experiments.tex
Edits in experiments.tex

\section{Evaluation}
\begin{itemize}
    \item goals of evaluation: Compare with NonDex and Deflaker
    \item Quantitative comparison: \theDeterminismChecker finds all bugs reported by NonDex and Deflaker?
    \item Qualitative study of the issues discovered.
    \item System info: 2.3 GHz Intel Core i5, 8 GB 2133 MHz
\end{itemize}

\subsection{Running NONDEX on Randoop}
To evaluate how existing tools perform on large programs, we ran the tool \href{https://github.com/TestingResearchIllinois/NonDex}{NONDEX~\cite{nondex}} on 
\href{https://github.com/randoop/randoop}{Randoop~\cite{randoop}}.
We followed the instructions to build the project with the gradle plugin. 
NONDEX terminated in approximately 20 seconds and didn't report any flaky tests.
\todo{check if the bugs discovered by \theDeterminismChecker have test coverage}
\todo{We investigated the tests covering code that \theDeterminismChecker reported as nondeterministic.
If code is covered by tests, NONDEX couldn't discover it. Else, its a limitation of NONDEX}.
This indicates that the additional programmer effort required by \theDeterminismChecker is justified
as our tool discovers non-trivial issues and doesn't depend on code coverage or other runtime heuristics.

\subsection{NONDEX case study}
Methodology:
\begin{itemize}
    \item Objective: Measure recall.
    \item Benchmarks from NONDEX paper.
    \item That paper gives flaky test class and source of flakiness (nondeterministic method call).
    \item Look at the source method under test.
    \item annotate the local arrays and collections (This has been mostly sufficient for recall)
    \item exceptions: unbuildable handlebars
    \item the reported source of nondeterminism couldn't be found in the source code.
    \item \todo{P4, P12 and P21}
\end{itemize}

>>>>

\section{Comparison to previous work}

The state of the art in flaky test detection is NonDex~\cite{nondex}.
\Cref{sec:related} explains how NonDex works.

\begin{itemize}
    \item goals of evaluation: Compare with NonDex and Deflaker
    \item Quantitative comparison: \theDeterminismChecker finds all bugs reported by NonDex and Deflaker?
    \item Qualitative study of the issues discovered.
    \item System info: 2.3 GHz Intel Core i5, 8 GB 2133 MHz
\end{itemize}

\subsection{Case study with NonDex}\label{sec:nondex-randoop}

We ran NonDex on the same commit of Randoop as we used for the case study
of \cref{sec:case-study}.  This version contains 3 nondeterminism bugs that
\ourTool found.

We modified Randoop by deleting tests that were skipped by its buildfile,
because the NonDex gradle plugin does not respect those settings.

After that, NonDex ran without problems on Randoop.
It terminated in approximately 20 seconds and reported no flaky tests.

\todo{check if the bugs discovered by \theDeterminismChecker have test coverage}
\todo{We investigated the tests covering code that \theDeterminismChecker reported as nondeterministic.
If code is covered by tests, NONDEX couldn't discover it. Else, its a limitation of NONDEX}.

\subsection{\OurTool on NonDex benchmarks}\label{sec:nondex-benchmarks}

\Cref{sec:nondex-randoop} shows that \ourTool finds errors that NonDex does not.

Methodology:
\begin{itemize}
    \item Objective: Measure recall.
    \item Benchmarks from NONDEX paper.
    \item That paper gives flaky test class and source of flakiness (nondeterministic method call).
    \item Look at the source method under test.
    \item annotate the local arrays and collections (This has been mostly sufficient for recall)
    \item exceptions: unbuildable handlebars
    \item the reported source of nondeterminism couldn't be found in the source code.
    \item \todo{P4, P12 and P21}
\end{itemize}
